---
title: "EDA to Improve Departure Delay"
author: "Ningkai Zheng"
output:
  html_document:
    theme: yeti
    highlight: pygments
    toc: yes
    number_sections: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

# Introduction

This is an exploratory data analysis for the __NYC Flights__, intending to improve departure delays. We provide several constructive suggestions at the end of the report.

## Load all the packages that will be needed during this project
```{r message=FALSE, warning=FALSE, results='hide'}
library(tidyverse)
library(xray)
library(dlookr)
library(scales)
library(lubridate)
library(corrplot)
```

We use the `multiplot` function, courtesy of [R Cookbooks](http://www.cookbook-r.com/Graphs/Multiple_graphs_on_one_page_(ggplot2)/) to create multi-panel plots.

```{r, include=FALSE}
# Multiple plot function
#
# ggplot objects can be passed in ..., or to plotlist (as a list of ggplot objects)
# - cols:   Number of columns in layout
# - layout: A matrix specifying the layout. If present, 'cols' is ignored.
#
# If the layout is something like matrix(c(1,2,3,3), nrow=2, byrow=TRUE),
# then plot 1 will go in the upper left, 2 will go in the upper right, and
# 3 will go all the way across the bottom.
#
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)

  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)

  numPlots = length(plots)

  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols))
  }

 if (numPlots==1) {
    print(plots[[1]])

  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}
```

## Read the related files

We got the following data sets to analyse the departure delay from several dimensions.

```{r}
flights=read.csv("flights.csv")
airports=read.csv("airports.csv")
airlines=read.csv("airlines.csv")
planes=read.csv("planes.csv")
weather=read.csv("weather.csv")
```

## Overview of the data
```{r message=FALSE, warning=FALSE, results='hide'}
summary(flights)
summary(airports)
summary(airlines)
summary(planes)
summary(weather)
```

```{r message=FALSE, warning=FALSE, results='hide'}
glimpse(flights)
glimpse(airports)
glimpse(airlines)
glimpse(planes)
glimpse(weather)
```

We find:

- `flights` contains the majority of useful information we will analyse, while other data sets are linked to it by several keywords.
- `airports` and `flights` are connected by `faa` (`origin, dest` in `flights`).
- `airlines` and `flights` are connected by `carrier`.
- `planes` and `flights` are connected by `tailnum`.
- `weather` and `flights` are connected by `origin` and `time_hour`.
- The departure delay range from -43 to 1301 minutes.

## Find problematic variables
```{r message=FALSE, warning=FALSE, results='hide'}
xray::anomalies(flights)
xray::anomalies(airports)
xray::anomalies(planes)
xray::anomalies(weather)
xray::anomalies(airlines)
```

Using `anomalies()` function, we find that `year` in `flights`, `speed` in `planes`, and `precip` and `year` in `weather` seem to be problematic variables.

- `year` in `flights` and `weather` is detected as a problematic variable because it only has one distinct value, which is `2013`. This is not an issue but a hint  about the year of flights and weather we are going to analyse.
- Around 99.31% of values in the `speed` column in `planes` are NA, which means we are not able to find the relationship between the cruising speed of planes and departure delays. But this won't affect other analyses.
- Around 93.3% of values in the `precip` column in `weather` are zero, which is quite normal because this only indicates no precipitation.
- We can also notice that `minute` in `flights` has 18% of zero values, which suggests the flights scheduled to depart on the hour. Plus, 79.56% of the variable `wind_gust` in `weather` have NA values, which will limit the analysis of the relationship between gust speed and departure delay.

## Find outliers

```{r message=FALSE, warning=FALSE, results='hide'}
diagnose_outlier(flights)
diagnose_outlier(airports)
diagnose_outlier(planes)
diagnose_outlier(weather)
```

Although some variables have outliers, such as `dep_delay` and `arr_delay`, we will not remove these outliers because it’s essential to use extreme values to analyse the causation of departure delay.

# Study the effect of airports

The departure delay can be affected by the origin airports. There are total 3 distinct origin airports as shown in the `anomalies()` by qDistinct.

Let's start with a general overview of the flights and departure delays at each of the three airports.

```{r}
flights %>%
  group_by(origin) %>%
  tally()
```

__Total number of flights:__ EWR > JFK > LGA.

```{r}
flights %>%
  ggplot(aes(x=dep_delay)) +
  geom_histogram(fill="yellow",binwidth=50,color="grey") +
  facet_wrap(~origin) +
  labs(x="Departure delay", y="Flights count") +
  theme_bw(base_line_size=0)
```

Happily, most flights in the three airports were not delayed. 

Do different airports behave differently concerning delayed flights? Let's filter out the undelayed flights and plot the graph again.

```{r}
flights %>%
  filter(dep_delay>0) %>%
  ggplot(aes(x=dep_delay)) +
  geom_histogram(fill="yellow",binwidth=50,color="grey") +
  facet_wrap(~origin) +
  labs(x="Departure delay", y="Flights count") +
  theme_bw(base_line_size=0)
```

Departure delays of the three airports show a similar distribution, while the amount of delayed flights varies considerably among the airports, as shown below.

```{r}
flights %>%
  group_by(origin,dep_delay>0) %>%
  tally()
```

__The amount of delayed flights:__ EWR(52414) > JFK(41833) > LGA(33498).

But where the total number of flights varies, it is not reasonable to use absolute numbers for comparison. Let's go deeper into the percentage of delayed flights of each airport.

```{r}
flights %>%
  group_by(origin,dep_delay>0) %>%
  tally() %>%
  mutate(percentage=percent(n/sum(n)))
```

__The percentage of delayed flights:__ EWR(45%) > JFK(38%) > LGA(33%).

It can be seen that there is a correlation between delays and the total number of flights. In other words, the occurrence of departure delays depends on how busy the airport is. We will further analyse the influence of busyness across time.

# The influence of busyness across time

## Busyness across a day

Let's compare the total number of flights and the total number of departure delays for each hourly period during the year.

```{r}
(p_total=flights %>%
  group_by(hour,origin) %>%
  tally() %>%
  ggplot(aes(hour,n,color=origin)) +
  geom_point(size=4,alpha=0.7) +
  labs(x="Hour of a day",y="Number of flights") +
  scale_x_continuous(breaks=seq(0,24,by=1)) +
  scale_color_manual(values=c("#FF665A","#7D6B7D","#FFF587")) +
  theme_bw() +
  theme(legend.title=element_blank(),legend.position="top"))
```

Flights are scheduled between 5 am and 11 pm.

The trend of flights across a day:
From 5 am to 6 am, the flights increase sharply and reach the summit at 6 am, after which the flights gradually decrease until 11 am and then slowly increase until 5 pm, followed by a rapid decrease to the end of the day.

```{r, fig.cap="Figure 1"}
flights_hour=flights %>%
  group_by(hour,origin) %>%
  tally()

flights_hour_delay=flights %>%
  filter(dep_delay>0) %>%
  group_by(hour,origin) %>%
  tally()

merge_hour=left_join(flights_hour,flights_hour_delay,by=c("hour","origin"))

p_total=p_total +
  coord_cartesian(ylim=c(0,12000))

p_percent=merge_hour %>%
  mutate(percent_delay=(n.y/n.x)) %>%
  ggplot(aes(hour,percent_delay,color=origin)) +
  geom_point(size=4,alpha=0.7) +
  labs(x="Hour of a day",y="Percent of delayed flights") +
  scale_x_continuous(breaks=seq(0,24,by=1)) +
  scale_y_continuous(labels=percent) +
  coord_cartesian(ylim=c(0,0.7)) +
  scale_color_manual(values=c("#FF665A","#7D6B7D","#FFF587")) +
  theme_bw() +
  theme(legend.position="none")

layout=matrix(c(1,2),2,1,byrow=FALSE)
multiplot(p_total,p_percent,layout=layout)
```

There is __no clear link__ between the total number of flights and the percentage of delayed flights across a day. Maybe we will be able to analyse this more accurately when we have access to data on the number of flights arriving at these airports.

However, we notice that the proportion of delayed flights tends to increase gradually over the day. The reason behind this may be the accumulation of flights leading to a variety of problems.

## Busyness across the year

First, plot the flights of all three airports across the year.

```{r}
(p1=flights %>%
  mutate(flight_date=ymd_hms(time_hour)) %>%
  ggplot(aes(flight_date,fill=(dep_delay>0))) +
  geom_histogram(bins=120,color="black") +
  labs(x="Year 2013",y="Flights") +
  theme_bw() +
  scale_fill_discrete(labels=c("Not delayed","Delayed")) +
  theme(legend.position = "top", legend.title=element_blank()))
```

If the percentage of delayed flights correlates with the total flights in this graph, we can conclude that flights from all three airports can affect each other, but the graph doesn't show any signs of this. We are going to analyse the three airports separately.

Plus, we note that the percentage of delayed flights is high in July and December and decreases between September and November, indicating seasonal influence across the year, which we will discuss later.

## Flights in EWR, JFK and LGA Airport across the year

Considering seasonal effects, we only extract data from January and February to analyse the effect of busyness in each airport.

```{r}
flights %>%
  mutate(flight_date=ymd_hms(time_hour)) %>%
  filter(year(flight_date)==2013,month(flight_date)<3, origin=="EWR") %>%
  ggplot(aes(flight_date,fill=(dep_delay>0))) +
  geom_histogram(bins=60,color="black") +
  labs(x="Jan-Feb 2013",y="EWR Airport") +
  theme_bw() +
  scale_fill_discrete(labels=c("Not delayed","Delayed")) +
  theme(legend.position = "top", legend.title=element_blank())
```

```{r}
flights %>%
  mutate(flight_date=ymd_hms(time_hour)) %>%
  filter(year(flight_date)==2013,month(flight_date)<3, origin=="JFK") %>%
  ggplot(aes(flight_date,fill=(dep_delay>0))) +
  geom_histogram(bins=60,color="black") +
  labs(x="Jan-Feb 2013",y="JFK Airport") +
  theme_bw() +
  scale_fill_discrete(labels=c("Not delayed","Delayed")) +
  theme(legend.position = "top", legend.title=element_blank())
```

```{r}
flights %>%
  mutate(flight_date=ymd_hms(time_hour)) %>%
  filter(year(flight_date)==2013,month(flight_date)<3, origin=="LGA") %>%
  ggplot(aes(flight_date,fill=(dep_delay>0))) +
  geom_histogram(bins=60,color="black") +
  labs(x="Jan-Feb 2013",y="LGA Airport") +
  theme_bw() +
  scale_fill_discrete(labels=c("Not delayed","Delayed")) +
  theme(legend.position = "top", legend.title=element_blank())
```

There is __no obvious relationship__ between busyness and departure delay, even some periods with fewer flights have a larger percentage of departure delays.

# Seasonal effects

We got the `weather` data to analyse seasonal effects.

## Merge the data

```{r}
weather_to_merge=weather[,c(1,9,10,12,14,15)]

merge_flights=left_join(flights,weather_to_merge,
                        by=c("origin","time_hour"))

merge_flights=na.omit(merge_flights,col=c("precip","visib",
                                          "wind_dir","wind_speed"))
```

Correlation overview
```{r}
merge_flights %>%
  select(dep_delay,precip,visib,wind_dir,wind_speed) %>%
  cor() %>%
  corrplot(type="lower",tl.srt=45,tl.col=1)
```

The precipitation and visibility are two possible factors that can significantly affect the departure delay.

## Analyse the weather effects

Plot the precipitation and visibility across the year, and compare it with the flights across the year.

```{r warning=FALSE}
p1=p1 +
  theme(legend.position="none") +
  labs(x=NULL)

p2=weather %>%
  mutate(month_day=ymd(paste(year,month,day,sep="/"))) %>%
  group_by(month_day) %>%
  ggplot(aes(x=month_day,y=precip,fill=origin)) +
  geom_histogram(stat="identity") +
  labs(x="Year 2013",y="Precipitation") +
  scale_x_date(breaks=date_breaks("1 month"),labels=date_format("%m-%d")) +
  scale_fill_manual(values=c("#FF665A","#7D6B7D","#FFF587")) +
  theme_bw() +
  theme(legend.position="none")

layout=matrix(c(1,2),2,1,byrow=FALSE)
multiplot(p1,p2,layout=layout)
```

```{r warning=FALSE}
p3=weather %>%
  mutate(month_day=ymd(paste(year,month,day,sep="/")),
         visibility=(10-visib)) %>% # make the graph more clear
  group_by(month_day) %>%
  ggplot(aes(x=month_day,y=visibility,fill=origin)) +
  geom_histogram(stat="identity") +
  labs(x="Year 2013",y="Counter Visibility") +
  scale_x_date(breaks=date_breaks("1 month"),labels=date_format("%m-%d")) +
  scale_fill_manual(values=c("#FF665A","#7D6B7D","#FFF587")) +
  theme_bw() +
  theme(legend.position="none")

layout=matrix(c(1,2),2,1,byrow=FALSE)
multiplot(p1,p3,layout=layout)
```

We can observe a correlation between precipitation and visibility and the percentage of delayed flights. The less rainfall or the better the visibility, the lower the percentage of flight delays will be. And only prolonged periods of good weather can significantly impact the percentage of flight delays, which can explain the drop in the percentage of flight delays between September and November. With the ever-changing weather, even with brief periods of good weather, the percentage of flight delays will remain largely unaffected. (The *Delayed Percent vs Weather* sheet in Tableau presents this relationship more clearly)

## Actions of the airports

Since the weather has impacts on flight delays, have the airline systems taken certain measures in response?

```{r, fig.cap="Figure 2"}
visibimage=merge_flights %>%
  group_by(visib) %>%
  tally() %>%
  ggplot(aes(visib,n)) +
  geom_point() +
  labs(x="Visibility",y="Flights count") +
  theme_bw()

precipimage=merge_flights %>%
  group_by(precip) %>%
  tally() %>%
  ggplot(aes(precip,n)) +
  geom_point()+
  labs(x="Precipitation",y="Flights count") +
  theme_bw()

layout=matrix(c(1,2),2,1,byrow=FALSE)
multiplot(visibimage,precipimage,layout=layout)
```

Most of the flights were scheduled in periods with visibility=10 and precipitation=0.

We can conclude that the airline systems were using accurate weather forecasting systems and scheduling appropriate flights according to it, which they are supposed to keep in the future.

When it comes to the airline system, the impact of the carrier is significant. We are going to analyse the difference in departure delay among the carriers.

# Influence of carrier

First, we need to know the flights per carrier.

```{r}
flights %>%
  group_by(carrier) %>%
  tally() %>%
  ggplot(aes(x=reorder(carrier,n),y=n)) +
  geom_bar(stat="identity") +
  geom_text(aes(label=n),nudge_y=2500) +
  labs(x="Carrier",y="Number of flights") +
  coord_flip() +
  theme_bw()
```

Then, find the percentage of delays for each carrier.

```{r}
flight_carrier=flights %>%
  group_by(carrier) %>%
  tally()

flight_carrier_delay=flights %>%
  filter(dep_delay>0) %>%
  group_by(carrier) %>%
  tally()

merge_carrier=left_join(flight_carrier,flight_carrier_delay,by="carrier")

merge_carrier[is.na(merge_carrier)]=0

(merge_carrier=merge_carrier %>%
  mutate(percent_delay=percent(n.y/n.x)) %>%
  arrange(percent_delay))
```

Plot the box plot of departure delay for each carrier and highlight the carriers with a large number of flights and a relatively small percentage of delays.

```{r, fig.cap="Figure 3"}
flights %>%
  ggplot(aes(y=carrier,x=dep_delay,
             color=carrier %in% c("US", "AA", "MQ", "DL"))) +
  geom_boxplot(outlier.alpha=0.1) +
  labs(y="Carrier",x="Departure delay") +
  theme_bw(base_line_size=0) +
  scale_color_discrete(labels=c("Others","More flights and less delays")) +
  theme(legend.position="top", legend.title=element_blank())
```

According to the table and graph, among carriers with a large number of flights and fewer delays, US perform the best and most stable in departure delay, while MQ, DL and AA should control the maximum length of delays, and WN, VX, EV, B6 and 9E should focus on reducing the percentage of departure delays.

# Influence of plane

First, have an overview of the data set `planes`.
```{r warning=FALSE}
xray::distributions(planes)
```

Different planes are of different types, engines, year of manufactured, etc. According to the `distributions()`, the type and engine number of almost all planes in the data are the same. The variable we can analyse is year of manufactured and seat number, which may affect the checking time before departure and eventually cause departure delay.

Merge and check the data.

```{r}
planes_to_merge=planes[,c(1,2,7)]
colnames(planes_to_merge)[2]="yearmanufactured"
merge_flights2=left_join(flights,planes_to_merge,by="tailnum")
merge_flights2=na.omit(merge_flights2,col=c("yearmanufactured","seats"))
```

## Influence of year manufactured

```{r}
merge_flights2 %>%
  group_by(yearmanufactured) %>%
  tally() %>%
  ggplot(aes(x=yearmanufactured,y=n)) +
  geom_point() +
  labs(y="Number of flights",x="Year manufactured") +
  scale_x_continuous(breaks=seq(1956,2013,by=5)) +
  theme_bw()
```

Planes manufactured between 1986 and 1996 and after 2009 have a similar number of flights, let's take them for analysis.

```{r}
flight_manuf=merge_flights2 %>%
  group_by(yearmanufactured) %>%
  tally()

flight_manuf_delay=merge_flights2 %>%
  filter(dep_delay>0) %>%
  group_by(yearmanufactured) %>%
  tally()

merge_manuf=left_join(flight_manuf,flight_manuf_delay,by="yearmanufactured")

merge_manuf[is.na(merge_manuf)]=0

merge_manuf %>%
  mutate(percent_delay=n.y/n.x) %>%
  ggplot(aes(x=yearmanufactured,y=percent_delay,size=n.x)) +
  geom_point(alpha=0.5) +
  labs(x="Year manufactured", y="Delayed %") +
  theme_bw() +
  scale_x_continuous(breaks=seq(1956,2013,by=5)) +
  theme(legend.position="none")
```

The percentage of delayed flights does not have a strong relationship with the year manufactured of the plane. Meanwhile, we notice that some older planes with a similar number of flights to new planes have a smaller percentage of delays.

```{r}
merge_flights2 %>%
  filter(yearmanufactured>=1986) %>%
  ggplot(aes(y=factor(yearmanufactured),x=dep_delay)) +
  geom_boxplot(outlier.alpha = 0.1) +
  labs(y="Year Manufatured",x="Departure Delay") +
  theme_bw(base_line_size=0)
```

Planes manufactured in recent years perform more stably in the length of departure delay than older ones. Carriers who need to control their length of departure delay should consider using more planes manufactured in recent years.

## Influence of seat number (i.e. plane size)

```{r}
merge_flights2 %>%
  group_by(seats) %>%
  tally() %>%
  ggplot(aes(x=seats,y=n)) +
  geom_point() +
  labs(y="Number of flights",x="Seat number") +
  scale_x_continuous(breaks=seq(0,500,by=50))+
  theme_bw()
```

The seat number of planes varies among the flights.

```{r}
flight_seat=merge_flights2 %>%
  group_by(seats) %>%
  tally()

flight_seat_delay=merge_flights2 %>%
  filter(dep_delay>0) %>%
  group_by(seats) %>%
  tally()

merge_seat=left_join(flight_seat,flight_seat_delay,by="seats")

merge_seat[is.na(merge_seat)]=0

merge_seat %>%
  mutate(percent_delay=n.y/n.x) %>%
  ggplot(aes(x=seats,y=percent_delay,size=n.x)) +
  geom_point(alpha=0.5) +
  labs(x="Seat number", y="Delayed %") +
  theme_bw() +
  theme(legend.position="none")
```

The percentage of delayed flights does not correlate with the seat number. 

```{r}
seat_count=merge_flights2 %>%
  group_by(seats) %>%
  tally()

merge_flights2 = left_join(merge_flights2,seat_count,by="seats")
```

```{r}
merge_flights2 %>%
  filter(n>=5000) %>%
  ggplot(aes(factor(seats),dep_delay)) +
  geom_boxplot(outlier.alpha = 0.1) +
  labs(x="Seat number", y="Departure delay") +
  theme_bw(base_line_size=0) +
  coord_flip()
```

The stability of departure delay and seat number do not have a significant relationship either.

## Suggestions

__Effect of busyness__. Although the percentage of departure delays at each of the three airports respectively corresponded to their total number of flights, in subsequent in-depth studies, we did not find a strong correlation between the percentage of departure delays and the busyness of the airports. We need information not only on departures from the three airports, but also on arrivals at the three airports to explore this matter more accurately. However, we have seen an increasing trend in the percentage of flight delays throughout the day (`Figure 1`), we therefore recommend that when airports encounter problems with departure delays, in addition to *taking action as soon as possible*, they should also consider trying *not to disrupt flights in the next slot*.

__Effect of weather__. The proportion of flight delays declined during long periods of low rainfall and high visibility. To their credit, the airports and airlines *have done a great job with the weather impact on flights*, with most flights being scheduled in times of good visibility and no rainfall (`Figure 2`). 

__Effect of carrier__. US performs the best and most stable departure delay (`Figure 3`), while MQ, DL and AA should control the maximum length of delays, and WN, VX, EV, B6 and 9E should focus on reducing the percentage of departure delays. Combined with the analysis of the dashboard in Tableau, we find that the percentage of delays varies from one destination airport to another. As UA and WN airlines do not control their percentage of delays well, some destination airports with a higher volume of flights have a higher percentage of delays than others. US and AA airlines, on the other hand, have reduced the percentage of delays at some destination airports. Thus, we recommend PANYNJ to work more intensively with *US and AA Airways*.